### 2019-09-11 reports/thesis/chapters/2_dataCollection.tex
Revise

The results are shown in Figures \ref{fig:data_anovaAbsNoFilter} and \ref{fig:data_anovaAbsFilter} for the datasets \texttt{AbsNoFilter} and \texttt{AbsFilter} respectively. With shading correction, the within and between pixel variance became more similar. A difference between BW and linear shading correction was that for the black image, the $F$ statistic is closer to one for BW shading correction compared to linear shading correction. For the rest of the powers, linear shading correction outperformed BW shading correction. This shows that linear shading correction generalises to powers between zero and $P_\text{proj}$. Since beam extinction is avoided, black grey values in the obtained projection should not be possible. As a result, the linear shading correction is recommended for its good performance for various powers.

>>>>

The results are shown in Figures \ref{fig:data_anovaAbsNoFilter} and \ref{fig:data_anovaAbsFilter} for the datasets \texttt{AbsNoFilter} and \texttt{AbsFilter} respectively. With shading correction, the within and between pixel variance became similar. A difference between BW and linear shading correction was that for the black image, the $F$ statistic is closer to one for BW shading correction compared with linear shading correction. For the rest of the powers, linear shading correction outperformed BW shading correction. This shows that linear shading correction generalises to powers between zero and $P_\text{proj}$. Since beam extinction is avoided, black grey values in the obtained projection should not be possible. As a result, the linear shading correction is recommended for its good performance for various powers.
